\section{Introduction}
Video super-resolution reconstructs an HR video sequence from an LR observation. Unlike single-image super-resolution, VSR must recover fine image structures while also using temporal redundancy across neighboring frames. This makes the task a balance between spatial reconstruction, perceptual sharpness, and temporal stability. Classical interpolation methods are fast and stable but cannot hallucinate missing high-frequency details. Learned image SR methods such as SRCNN~\cite{dong2015srcnn}, SRGAN~\cite{ledig2017srgan}, and EDSR~\cite{lim2017edsr} improve spatial reconstruction, but frame-independent processing often ignores temporal coherence. Modern VSR models therefore introduce motion alignment and recurrent propagation, as represented by EDVR~\cite{wang2019edvr}, TDAN~\cite{tian2020tdan}, BasicVSR~\cite{chan2021basicvsr}, and BasicVSR++~\cite{chan2022basicvsrpp}.

This project implements and evaluates a practical VSR pipeline in three parts. First, we build classical and simple neural baselines to understand the behavior of interpolation, shallow CNN reconstruction, and naive temporal fusion. Second, we reproduce pretrained SOTA models: Real-ESRGAN~\cite{wang2021realesrgan} for perceptual enhancement and BasicVSR/BasicVSR++ for video-specific temporal propagation. Third, motivated by the fact that perceptual models can introduce hallucinated texture while distortion-oriented VSR can appear smooth, we design an adaptive hybrid method that combines the stable structure of BasicVSR++ with selected Real-ESRGAN details.

Our experiments cover the mandatory sample and wild datasets, and a larger standard benchmark using the full REDS validation split~\cite{nah2019reds}. We report PSNR and SSIM~\cite{wang2004ssim} for pixel fidelity, LPIPS~\cite{zhang2018lpips} and FID for perceptual quality, and a tLPIPS-style temporal metric inspired by temporally coherent video restoration~\cite{chu2020tlpips}. Qualitative analysis includes flowcharts, rendering comparisons, zoom-in patches, and processed videos.
