\section{Discussion}
The experiments show that VSR quality depends on both temporal modeling and the chosen objective. PSNR/SSIM favor GT-aligned reconstructions, where BasicVSR++ is strongest. This is expected because BasicVSR++ explicitly aggregates temporally aligned information, allowing it to recover details while preserving the structure of the original HR frame. In contrast, perceptual metrics partially favor visually sharper outputs, where Real-ESRGAN becomes more competitive. Its lower PSNR/SSIM should not be interpreted as complete failure; rather, it reflects that GAN-style restoration may generate plausible textures that are not pixel-identical to GT.

The adaptive hybrid demonstrates that a simple pixel-wise mask can combine these behaviors without retraining. It does not exceed BasicVSR++ on distortion metrics, but it remains very close while slightly improving LPIPS on the full REDS validation benchmark. This makes Part~3 useful as an analysis-driven extension: it exposes the perception-distortion trade-off and gives a controllable mechanism for deciding where perceptual enhancement should be trusted.

The qualitative figures also show why a single metric is insufficient. If we only inspect PSNR and SSIM, Real-ESRGAN appears weak; however, rendering comparisons reveal sharper edges and more natural textures in several regions. If we only inspect perceptual sharpness, BasicVSR++ may appear slightly smooth, but the zoom patches and full-frame comparisons show that its structures are more faithful to GT. The hybrid method is therefore best interpreted as a conservative fusion strategy: it is not a new SOTA model, but a lightweight mechanism for testing how much perceptual detail can be added without destroying temporal and pixel fidelity.

There are also important caveats. First, our tLPIPS is warpless and does not explicitly compensate for motion; therefore, it should be read as a flicker proxy rather than a perfect temporal consistency metric. Second, full REDS validation used BasicVSR++ rather than both BasicVSR and BasicVSR++ because of computational cost. We consider this acceptable because BasicVSR++ is the stronger representative and BasicVSR was already reproduced on the mandatory sample datasets. Third, the adaptive mask is hand-crafted. It is interpretable and cheap, but it cannot learn semantic uncertainty such as text, faces, or repeated structures.

\section{Conclusion}
We completed all three required parts of the VSR project. Part~1 established classical and shallow CNN baselines. Part~2 reproduced pretrained Real-ESRGAN, BasicVSR, and BasicVSR++ pipelines. Part~3 introduced an adaptive hybrid refinement that fuses BasicVSR++ and Real-ESRGAN to explore the perception-distortion trade-off. Quantitative and qualitative results on mandatory data and full REDS validation show that BasicVSR++ is the best distortion-oriented method, Real-ESRGAN is useful for perceptual detail, and the adaptive hybrid provides a low-cost extension that stays close to BasicVSR++ while incorporating controlled perceptual enhancement.

\section*{Limitations and Future Work}
Our SRCNN baseline is shallow and uses limited weights, so it does not fully represent modern image SR. The temporal averaging baseline has no motion compensation and is mainly a diagnostic failure case. Real-ESRGAN is frame-independent and may flicker. The adaptive hybrid uses hand-crafted masks rather than learned uncertainty estimates. Future work could train a lightweight temporal fusion network, add optical-flow-aligned tLPIPS, evaluate additional benchmarks such as Vimeo-90K, and explore generative priors such as diffusion, ControlNet, or flow matching with explicit temporal constraints. A stronger version of Part~3 could also learn the fusion mask from validation data, using PSNR/SSIM, LPIPS, and temporal losses jointly.
